\documentclass[letterpaper,11pt]{article}

%
% Package Imports
%
\usepackage[top=1.2cm, bottom=1.2cm, left=1.8cm, right=1.8cm]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xifthen}
\usepackage{etoolbox}
\usepackage{ragged2e}
\usepackage{tabularx}
\usepackage{enumitem}

\pagestyle{empty}

%
% Colors
%
\definecolor{primary}{HTML}{2C2C2C} 
\definecolor{heading}{HTML}{5D5D5D}
\definecolor{subheading}{HTML}{6A6A6A}
\definecolor{accent}{HTML}{263238}

%
% Fonts / Styles
%
\setmainfont[Color=primary]{Avenir Next}
\titleformat{\section}{\Large\scshape \RaggedRight}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{15pt}{8pt}

\newcommand*{\demibold}{\fontspec[Color=heading]{Avenir Next Demi Bold}}
\newcommand*{\medium}{\fontspec[Color=heading]{Avenir Next Medium}}
\newcommand*{\ultralight}{\fontspec[Color=heading]{Avenir Next Ultra Light}}

%
% Helper Style Commands
%
\newcommand*{\employerstyle}[1]{\large\demibold[Color=heading]\selectfont{#1}\normalfont}
\newcommand*{\datestyle}[1]{\medium\mdseries{#1}\normalfont}
\newcommand*{\jobstyle}[1]{\demibold[Color=subheading]\fontsize{10.5pt}{11pt}\selectfont{#1}\normalfont}
\newcommand*{\locationstyle}[1]{\medium\mdseries\emph{#1}\normalfont}

\newcommand*{\skillstyle}[1]{\fontsize{11pt}{11pt}\demibold{#1}\normalfont}

\newcommand*{\firstnamestyle}[1]{\medium\Huge\selectfont{#1}\normalfont}
\newcommand*{\lastnamestyle}[1]{\demibold\Huge\selectfont{\textsc{#1}}\normalfont}


%
% Helpers
%

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=1.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{-1pt}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\textendash}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeEntry}[4]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{\textwidth - 1.5mm}{X@{\hspace{60pt}}r}
      \employerstyle{#1} & \datestyle{#2} \\
      \jobstyle{#3} & \locationstyle{#4} \\
    \end{tabularx}\vspace{-6pt}
}

\newcommand{\resumeEntrySkill}[2]{
  \item[]\small{
    \skillstyle{#1}: {#2\vspace{-6pt}}
  }
}

% Header
\newcommand{\header}[3]{
  \begin{tabularx}{.95\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \firstnamestyle{Dave} \lastnamestyle{Walker}
      \end{tabular}
    } & {
      \begin{tabular}[c]{r@{\hspace{1.5em}}}
        {\small#1} \\
        {\small#2} \\
        {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}


%
% Document
%
\begin{document}
  \header{me@davewalker.dev}{609-933-5284}{Lakewood, Colorado}

\section{Professional Summary}
  \RaggedRight{
    Proven \emph{Software Engineering Manager} applying results-oriented and customer focus to the entire software development lifecycle.
    Skilled in enabling core architectural and product teams to deliver software customers love.
    Established leader specializing in project management leading cross-functional teams in a fast-paced environment. 
      Passionate drive for establishing high quality software practices, growing development teams, and product direction to ensure delivery of exceptional software.
    }

\section{Experience}
  \resumeEntryStart
    \resumeEntry
      {Workiva}{February 2019 \textemdash ~Present}
      {Software Engineering Manager}{Denver, Colorado}
    \resumeItemListStart
      \resumeItem {Led team responsible for core architecture and design of the foundation experiences of the Workiva Platform (\href{https://www.workiva.com/platform}{workiva.com/platform}).}
      \resumeItem {Successfully delivered platform API, enabling partners and internal teams to extend the core product.}
      \resumeItem {Foster a highly performant and collaborative culture, promoting knowledge sharing and skill development.}
      \resumeItem {Mentor and coach team members, fostering personal and professional growth.}
      \resumeItem {Collaborate with cross-functional teams to develop and define project scope, deliverables, and timelines.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntry
      {Workiva}{July 2018 \textemdash ~February 2019}
      {Senior Software Engineer}{Denver, Colorado}
    \resumeItemListStart
      \resumeItem {Provided technical guidance and mentoring to new developers.}
      \resumeItem {Developed annotation framework, including next generation financial evidence attachment feature.}
      \resumeItem {Expanded functionality of document packaging for the SEC Filing experience.}
      \resumeItem {Worked with cross-organization development teams to ensure effective delivery of projects.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntry
      {nio Innovation, LLC}{February 2017 \textemdash ~June 2018}
      {Senior Software Engineer}{Broomfield, Colorado}
    \resumeItemListStart
      \resumeItem {Inventor of Pubkeeper (\href{http://niolabs.com/product/pubkeeper}{niolabs.com/product/pubkeeper}) a patent-abandoned communications platform that enables disparate devices to operate in a pub/sub environment.}
      \resumeItem { Ported core IoT product from Python to C, with a goal to establish a platform for
embedded deployments via MbedOS and other RTOS.}
      \resumeItem {Converted cloud infrastructure between Cloud Service providers, abstracting implementation with Kubernetes, Helm, and Vault.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  \resumeEntryStart
    \resumeEntry
      {Symplicity}{June 2012 \textemdash ~February 2017}
      {Software Engineering Manager}{Arlington, Virginia}
    \resumeItemListStart
      \resumeItem {Initial creator and lead for Residence (\href{http://symplicity.com/residence}{symplicity.com/residence}).}
      \resumeItem {Provide strategic decisions with executive management that set product direction.}
      \resumeItem {Engage with clients to understand and learn requirements to plan future roadmap.}
      \resumeItem {Keep product and development team on-time, and within budget.}
      \resumeItem {Managed team of developers to ensure focus on product direction and delivery.}
    \resumeItemListEnd
  \resumeEntryEnd
\section{Education}
  \resumeEntryStart
    \resumeEntry
    	{Rochester Institute of Technology}{May 2008}
    	{B.Sc Applied Networking and Systems Administration}{Rochester, NY}
   \resumeEntryEnd
  
\section{Skills}
  \resumeEntryStart
    \resumeEntrySkill{Management}{Project Management, Career Guidance \& Development, Agile \& Kanban Processes}
    \resumeEntrySkill{Languages}{Golang, Dart, C, PHP}
  \resumeEntryEnd
  
\end{document}
